Usage metrics

### 2020-12-20 analysis/usage.Rmd
changes

```{r read, message=TRUE, include=F}
# This test should allow to re-run the whole script without reading the
# data again from disk. It assumes the data doesn't change.
if (exists("E") == FALSE) {
  read_fst(eval_calls_path) %>% as_tibble() -> E_raw
  read_fst(corpus_path) %>% as_tibble() -> C_raw
  read_csv(eval_static_path) %>% semi_join(C_raw, by = "package") -> P
}
```

```{r select-columns, message=TRUE, warning=FALSE, include=FALSE}
E_raw %>% select(
  run_package = package, #      The package which was run to trigger the eval
  ev_variant = eval_function, # Which eval variant was called
  duplicates = nb_ev_calls, #   Number of identical eval calls (weight)
  src_ref = eval_call_srcref, # Source ref for the eval call site
  file, #                       Script file name (name of this run)
  ev_package = eval_source, #   Package of the call site
  arg_size = expr_resolved_length, #   Size in characters (unicode) of eval argument string
  ast_nodes = expr_resolved_nodes,
  type = expr_resolved_type_tag,
  opcodes = direct_interpreter_eval #  Count of the AST nodes traversed by the
) -> E #                               interpreter during eval (non-recursive).

>>>>

```{r read, message=TRUE, include=F}
read_fst(corpus_path) %>% as_tibble() -> C_raw
read_csv(eval_static_path) %>% semi_join(C_raw, by = "package") -> P

rebuild <- FALSE
# We only read the orignal evals_calls file if we don't have a summarized
# version stored on disk.  NOTE: the heuristic to detect changes is file
# size. If that fails, manually delete `.lock.fst`
if (file.exists("Data/.lock.fst")) {
  saved <- read.fst("Data/.lock.fst")[[1,1]]
  if (saved == file.size(eval_calls_path)) {
     read.fst("Data/E.fst") %>% as_tibble() -> E
  } else {
    rebuild <- TRUE
  }
}
if (rebuild) {
  read_fst(eval_calls_path) %>% as_tibble() -> E_raw
  E_raw %>% select(
    run_package = package, #      The package which was run to trigger the eval
    ev_variant = eval_function, # Which eval variant was called
    duplicates = nb_ev_calls, #   Number of identical eval calls (weight)
    src_ref = eval_call_srcref, # Source ref for the eval call site
    file, #                       Script file name (name of this run)
    ev_package = eval_source, #   Package of the call site
    arg_size = expr_resolved_length, #   Size in characters of argument 
    ast_nodes = expr_resolved_nodes, #   Size in AST Nodes
    type = expr_resolved_type_tag,   #   Argument type
    opcodes = direct_interpreter_eval #  Count of the AST nodes traversed by the
  ) %>% #                                interpreter during eval (non-recursive).
   mutate(across(where(is_character),as_factor)) -> E 
  write.fst(E, "Data/E.fst")
  sz <- file.size(eval_calls_path) %>% as_tibble()
  write.fst(sz,"Data/.lock.fst")
}
